Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2018-02-20 paper/1-catalog/twoface-catalog.tex
more refs and text

@@

As an initial use of the per-source posterior samplings, we use a hierarchical
Bayesian model to infer the parameters of the (assumed Gaussian) distribution
over the log-excess-variance parameter: $(\mu_y, \sigma_y)$.
This inference serves as a test-case for future work, where we intend to use the
independent posterior samplings to construct a hierarchical inference over
companion property distributions.
This is also a test of the visit velocity uncertainties reported in the \apogee\
data products: If the catalog uncertainties are significantly underestimated, we
expect the inferred log-excess-variance distribution parameters to tend towards
larger values.

In detail, we maximize the marginal likelihood of the population-level
parameters $\bs{\alpha} = (\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given
vector $\bs{\alpha}$ over the value of the default prior at the previously
assumed values, $\bs{\alpha}_0 = (\mu_{y,0}, \sigma_{y,0})$ (see
\sectionname~\ref{sec:initsampling}).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters
(\citealt{Hogg:2008,Foreman-Mackey:...}); we describe how to compute the
marginal likelihood in detail below.

@@

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
\todo{discussion about this}
\todo{some discussion of how this relates to empirical bayes?}

>>>>

\subsection{Implementation notes}

\todo{Nontrivial computation - details about running on cluster, TheJoker vs. emcee}

@@

As an initial use of the per-source posterior samplings, we use a hierarchical
Bayesian model to infer the parameters of the (assumed Gaussian) prior over the
log-excess-variance parameter, $(\mu_y, \sigma_y)$ (see
\tablename~\ref{tbl:params}).
This inference serves as a test-case for future work, where we intend to use the
independent posterior samplings to construct a hierarchical inference over
companion population properties.
This is also a test of the visit velocity uncertainties reported in the \apogee\
data products: If the catalog uncertainties are significantly underestimated, we
expect the inferred log-excess-variance distribution parameters to tend towards
larger values.

In detail, we maximize the marginal likelihood of the population-level
parameters $\bs{\alpha} = (\mu_y, \sigma_y)$.
We compute this marginal likelihood using the per-object posterior samples
re-weighted by the ratio of the value of the hyperprior evaluated at a given
vector $\bs{\alpha}$ over the value of the default prior at the previously
assumed values, $\bs{\alpha}_0 = (\mu_{y,0}, \sigma_{y,0})$ (see
\sectionname~\ref{sec:initsampling}).
This trick has been used in other hierarchical inferences as a way to
marginalize over the per-object parameters
(\citealt{Hogg:2010,Foreman-Mackey:2014}); we describe how to compute the
marginal likelihood in detail below.

@@

We use 1,825 stars with $>10$ visits and $\log g < 2$ (to avoid upper RGB stars
that have large intrinsic jitter) and maximize the above likelihood to determine
better hyperparameters for the log-excess-variance parameter distribution.
\figurename~\ref{fig:infer-jitter} shows the distribution corresponding to the
maximum-likelihood hyperparameters, $\alpha^* = (\mu_y^*, \sigma_y^*) = (9.50,
1.64)$.
\todo{Reactions to the inferred parameters?}
\todo{Discuss how this relates to empirical Bayes?}
